Title

### 2014-01-09 paper/paper.tex
Added a blurb about transfer entropy.
This blurb is probably too long for a 6 page paper. But we can cut it
down as we need to.
Added AAAI author kit files. Put paper into AAAI 'camera-ready' style.
According to

http://icwsm.org/2014/submitting/guidelines/

we should aim for 8 to 10 pages. We currently have 2.
Modified paper to be anonymous.
As per the Anonymity guidelines here:

http://icwsm.org/2014/submitting/guidelines/
Unify the notation for the weights across the community types.
Adding titles/authors and abstract slots

%%%%% Beginning of preamble %%%%%
\documentclass[12pt]{article}

%What kind of document (article) and what size
%Packages to load which give you useful commands
\usepackage{amssymb, amsmath, amsthm} 
\usepackage{epsfig,graphicx} 
\usepackage{caption}
\usepackage{subcaption}
\usepackage{authblk}
\usepackage{verbatim}

%Sets the margins
\textwidth = 6.5 in 
\textheight = 9 in 
\oddsidemargin = 0.0 in 
\evensidemargin = 0.0 in 
\topmargin = 0.0 in 
\headheight = 0.0 in 
\headsep = 0.0 in \parskip = 0.2in \parindent = 0.0in

\begin{document} 
\title{Working Title}

% \author[1]{David Darmon}
% \author[2]{Elisa Omodei}
% \author[3]{Cesar O. Flores}
% \author[4]{Lu\'is F. Seoane}
% \author[5]{Kevin Stadler}
% \author[6]{Jody Wright}
% \author[7]{Joshua Garland}
% \author[8]{Nix Barnett}
% \affil[1]{Department of Mathematics, University of Maryland, College Park}
% \affil[2]{ISC-PIF, LaTTiCe-CNRS, \'Ecole Normale Sup\'erieure, Paris}
% \affil[3]{School of Physics, Georgia Institute of Technology, Atlanta}
% \affil[4]{ICREA-Complex Systems Lab, Universitat Pompeu Fabra, Barcelona}
% \affil[5]{School of Philosophy, Psychology and Language Sciences, The University of Edinburgh, Edinburgh}
% \affil[6]{Department of Microbiology and Immunology, University of British Columbia, Vancouver}
% \affil[7]{Department of Computer Science, University of Colorado, Boulder}
% \affil[8]{Department of Mathematics and Complexity Sciences Center, University of California, Davis}

\date{\today} 
\maketitle

\abstract{Lorem ipsum}

\input{parts/intro.tex}
\input{parts/community.tex}

\bibliographystyle{plain}
\bibliography{references}

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{amssymb, amsmath, amsthm}
\usepackage{graphicx}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Input Your Paper Title Here)
/Author (John Doe, Jane Doe)
/Keywords (Input your paper’s keywords in this optional area)}

%%%%%%%%%%
% Section Numbers
% Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
\setcounter{secnumdepth}{0}

%%%%%%%%%%
% Body of Paper Begins
\begin{document}

% Title, Author, and Address Information
\title{Followers are not enough: Beyond structure in the detection of communities \\
Followers are not enough: Exploring the communities that exist beyond structure \\
Followers are Not Enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
Followers are not enough: Beyond structural communities in online social networks
 \\
 Followers are not enough: exploring communities beyond structure
\\
 }
  \author{David Darmon \\
 Address line\\
 Address line\\
 \And Elisa Omodei \\
 LaTTiCe (CNRS, ENS, Paris 3)\\
ISC-PIF\\
elisa.omodei@ens.fr \\
 \And 
 Joshua Garland\\
 University of Colorado at Boulder\\
Dept. of Computer Science
joshua.garland@colorado.edu}

\maketitle

\begin{abstract}
\begin{quote}
[[Joshua]]

[[David]]

[[Elisa]]

\end{quote}
\end{abstract}

\input{parts/intro.tex}
\input{parts/community.tex}
\input{parts/methods.tex}
\input{parts/results.tex}
\input{parts/discussion.tex}

\bibliography{references}
\bibliographystyle{aaai}
